Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

1) Explore use of Facebook AI Research's \verb|detectron| tool.  Specific
aims are to use \verb|detectron| to identify study-specific objects.
% classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in
% Figure \ref{fig:teaser}.

2) Investigate image processing at the pixel level.
Pilot testing found that \verb|detectron| under-segmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

\renewcommand{\labelenumi}{\alph{enumi}.}
\begin{enumerate}
\item
Identify the appropriate threshold value for a more accurate mask.
% We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value. [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]

@@

3) Compute a number of high-level metadata properties from the detected objects and image quality metrics.
% [*Test our ability to calculate] the following set of
% : 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.

4) Compare computed metadata properties with manually generated properties
when possible to assess the accuracy and effectiveness of automated 
methods.

>>>>

\begin{enumerate}
\item Explore use of Facebook AI Research's \verb|detectron| tool.  Specific
aims are to use \verb|detectron| to identify study-specific objects.
% classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in
% Figure \ref{fig:teaser}.

\item Investigate image processing at the pixel level.
Pilot testing found that \verb|detectron| under-segmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

%\renewcommand{\labelenumi}{\alph{enumi}.}
\begin{enumerate}
\item
Identify the appropriate threshold value for a more accurate mask.
% We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value. [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]

@@

\item Compute a number of high-level metadata properties from the detected objects and image quality metrics.
% [*Test our ability to calculate] the following set of
% : 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.

\item Compare computed metadata properties with manually generated properties
when possible to assess the accuracy and effectiveness of automated 
methods.
\end{enumerate}
